### 2013-08-15 Tex/chapters/results.tex
kleinere Korrekturen

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l r r r r r}
            \toprule
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \midrule
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
            \bottomrule
        \end{tabular}
        \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
        \label{tab:tauAndTeq}
    \end{table}\\
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}\].
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity, so that the
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
    \cite{Bootstrap}\\
    The bootstrapping method estimates error \(\Delta \overline{\avg{O}}\)
    by taking \(M\) random samples from the \(M\) measured values of \(O\),
    where the same value can be chosen more than once, calculating the
    estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
    times. Then the standard deviation of of the \(k\) calculated \(\avg{O_b}\)
    is taken as an estimate for \(\Delta \overline{\avg{O}}\).
    In this thesis the number of bootstrap samples is \(k = 200\).\\
    Note that while the error of \(\avg{O}\), \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
    \(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
    over different realizations of the random proximity graph, which are
    surely uncorrelated.
    Because every error mentioned in this thesis is of this type, it is not
    necessary to determine \(\tau\) for each observable. Therefore a good
    error estimate can be achieved by simple bootstrapping. Nevertheless one has
    to simulate enough uncorrelated states for each realization to keep
    the \(\Delta \overline{\avg{O}}\) small. For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot. Gnuplot is an open source plotting program, used for all plots
    and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.

>>>>

    For evaluation the Monte Carlo simulation is run until the system
    is equilibrated after \(t_{eq}\) sweeps. Then the simulation continues
    and the magnetization per site \(m=\frac{1}{N}\sum_i s_i\) and energy
    per site \(E=\frac{1}{N} H\) are calculated and saved for every
    \(2\tau\) sweeps, where \(\tau\) denotes the \emph{autocorrelation time}
    (see also \ref{sssec:eqtime}). The used values for different system sizes
    are listed in Tab.\ \ref{tab:tauAndTeq} in numbers of sweeps. Note that
    the \(t_{eq}\) values are generously rounded up to be on the safe side
    and the \(\tau\) values are determined as the maximum \(\tau\) over all
    simulated temperatures and disorder parameters \(\tau = \underset{T,\sigma}{\max} \{\tau_{T,\sigma}\}\)
    and rounded up to the next integer.
    \begin{table}[htbp]
        \center
        \begin{tabular}{l r r r r r}
            \toprule
            \(L\)    & 16 &  32 &  64 & 128 & 256\\
            \midrule
            \(\tau\) &  3 &   5 &   7 &  12 &  16\\
            \(t_{eq}\) & 40 & 100 & 100 & 200 & 600\\
            \bottomrule
        \end{tabular}
        \caption{Autocorrelation Times $\tau$ and Equilibration Times $t_{eq}$}
        \label{tab:tauAndTeq}
    \end{table}\\
    For every observable \(O\) the expected value \(\avg{O}\) is determined
    as the mean of \(N_{\mathrm{measure}}=10000\) measurements for \(L=16,32\)
    or \(N_{\mathrm{measure}}=5000\) for \(L=64,128\). The number of
    calculated sweeps totals to
    \[N_{\mathrm{sweeps}}=t_{eq}+2\tau N_{\mathrm{measure}}.\]
    The expected values \(\avg{O}\) for \(100\) different random proximity
    graphs with the same disorder parameter \(\sigma\) are then averaged to
    \(\overline{\avg{O}}\). Note that the signs \(\overline{\avg{\cdot}}\)
    are omitted in the following for the sake of simplicity, so that the
    it will be just called \(O\).\\
    Not only the seed to generate the new random
    realization of the proximity graph is changed, but also the seed for
    the random numbers used in the Monte Carlo simulation and during the
    generation of the random start configuration of the spins.\\
    The errors \(\Delta \overline{\avg{O}}\) are estimated by bootstrapping
    \cite{Bootstrap}\\
    The bootstrapping method estimates error \(\Delta \overline{\avg{O}}\)
    by taking \(M\) random samples from the \(M\) measured values of \(O\),
    where the same value can be chosen more than once, calculating the
    estimator \(\avg{O_b}\) of this bootstrap sample and doing this \(k\)
    times. Then the standard deviation of of the \(k\) calculated \(\avg{O_b}\)
    is taken as an estimate for \(\Delta \overline{\avg{O}}\).
    In this thesis the number of bootstrap samples is \(k = 200\).\\
    Note that while the error of \(\avg{O}\), \(\Delta \avg{O}\) is dependend on \(\tau\) \cite[p. 151]{Katzgraber2011}
    \(\Delta \overline{\avg{O}}\) is not directly, because it is averaged
    over different realizations of the random proximity graph, which are
    surely uncorrelated.
    Because every error mentioned in this thesis is of this type, it is not
    necessary to determine \(\tau\) for each observable. Therefore a good
    error estimate can be achieved by simple bootstrapping. Nevertheless one has
    to simulate enough uncorrelated states for each realization to keep
    the \(\Delta \overline{\avg{O}}\) small. For every determined value an
    error is calculated and given in the form \texttt{value(error of last digit)}.
    The errors of fit parameters are the asymptotic standard errors as calculated
    by gnuplot. Gnuplot is an open source plotting program, used for all plots
    and fits in this thesis \footnote{\url{http://gnuplot.info/}.}.
